\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics/npa.tex
Cite undergrads

    \caption{Frequency of navigations-per-adds when the goal was to add a specific course}
    \label{fig:navs-direct}
  \end{figure}

@@

  Browsing behavior was done as a direct inverse of  harder to detect than direct search behavior, because there  query behavioral patterns
  Discovery, browsing, exploring

@@

    \caption{Frequency of navigations-per-adds/bookmarks when the goal was to browse for courses}
    \label{fig:searchtypes}
  \end{figure}

  As expected, the 0-navs were mostly maincourses (62\%)

>>>>

    \caption{Frequency of navigations-per-adds when the goal was to \emph{add a specific course}}
    \label{fig:navs-direct}
  \end{figure}

@@

@@

    \caption{Frequency of navigations-per-add/bookmark when the goal was to \emph{browse for courses}}
    \label{fig:navs-browse}
  \end{figure}

  Browsing behavior was done as a direct inverse of direct searches, detecting searches that didn't specifically target any courses. This time, bookmarks were also counted in a user's flow of events (i.e. they are treated the same as an add), because bookmarking is also a goal of course browsing behavior.

  The results are shown in Figure \ref{fig:navs-browse}. The difference between these results and the initial combined results of \ref{fig:navs-combined} are more substantial than last time, and may defy expectations at first glance. While it may seem intuitive that browsed-for courses should have higher amounts of navigations, note that the graph itself is showing \emph{effectiveness} of such browsing. In this case, it makes sense that a significantly higher proportion of adds/bookmarks occur within zero navigations, because that indicates a high-level search and subsequent adds/bookmarks from that list instead of moving on to another search.

  As expected, and unlike the results of further direct-search analysis, the sections added/bookmarked when browsing within 0 navigations were mostly \emph{main} sections (only 37\% of them were subsections). This makes sense, as users may not be concerned with subsections if the goal of the browse is merely to mark interesting courses. This criterion saw more drastic drops in subsection amounts as well, as the number of navs increased: 5\% subsections for ${navs}=1$, and 4\% subsections for ${navs}=2$.

### 2016-04-13 analytics/usage.tex
linksearches graph
half of nps
Cite undergrads

In an attempt to exclude ``stale users,'' we can time-constrain our analysis. In the past month, there were 1,416 visitors to the site and 672 visitors \emph{with schedules}. However, this metric excludes data from seniors who did not have need for Skedge in the past month. Going back to November 3, 2015, course registration day ($\sim$5 months ago), we find 4,647 visitors to the site and 1322 visitors with schedules. Thus, we can estimate that the amount of users who have added courses with Skedge is about \textbf{one-fifth} of all undergraduates (6,046) at the College.

@@

  \end{tabular}
  \vspace{10pt}
  \caption{A sample of humorous searches}
  \label{fig:funny-queries}
\end{table}
\end{center}

@@

\begin{figure}[H]
  \centering
  \vspace{20pt}
    \begin{subfigure}[w]{14cm}
      \centering
      \includegraphics[width=1.00\textwidth]{images/graph/exports}
      \caption{Different types of schedule exporting over time} \label{fig:exports}
    \end{subfigure} \\
    \vspace{30pt}
    \begin{subfigure}[w]{14cm}
      \centering
      \includegraphics[width=1.00\textwidth]{images/graph/linksearches}
      \caption{Different types of ``link-search'' clicks over time, with manual instructor search included for comparison with clicking on an instructor's name} \label{fig:linksearches}
    \end{subfigure}

@@

\singlespacing
\begin{center}
\begin{tabular}{l}
  \hline
  141 users have linked Skedge to Facebook \\
  10,242 page views (256 page views/day)  \\
  10 pages/session (users cycle through tabs and go back to it) \\
  a 5\% bounce rate (users interact with it) \\
  67\% of visits being were returning visitors \\
  284 overlays onto friends’ schedules (2 per user) \\
  \hline
\end{tabular}
\end{center}
\doublespacing

>>>>

In an attempt to exclude ``stale users,'' we can time-constrain our analysis. In the past month, there were 1,416 visitors to the site and 672 visitors \emph{with schedules}. However, this metric excludes data from seniors who did not have need for Skedge in the past month. Going back to November 3, 2015, course registration day ($\sim$5 months ago), we find 4,647 visitors to the site and 1322 visitors with schedules. Thus, we can estimate that roughly \textbf{one-fifth} of all undergraduates (6,046 students) at the College have added courses on Skedge \cite{undergrads}.

@@

  \end{tabular}
  \vspace{10pt}
  \caption{A sample of some funny searches}
  \label{fig:funny-queries}
\end{table}
\end{center}

@@

\begin{figure}[H]
  \centering
    \begin{subfigure}[w]{14.5cm}
      \centering
      \includegraphics[width=1.00\textwidth]{images/graph/exports}
      \caption{Different types of schedule exporting over time} \label{fig:exports}
    \end{subfigure} \\

    \vspace{30pt}

    \begin{subfigure}[w]{14.5cm}
      \centering
      \includegraphics[width=1.00\textwidth]{images/graph/linksearches}
      \caption{Different types of ``link-search'' clicks over time, with manual instructor search included for comparison with clicking on an instructor's name} \label{fig:linksearches}
    \end{subfigure}

@@

{\renewcommand{\arraystretch}{1.5}
\singlespacing
\begin{center}
\begin{tabular}{l}
  \hline
  141 users have linked Skedge to Facebook \\
  10,242 page views (256 page views/day)  \\
  10 pages/session (users cycle through tabs and go back to it) \\
  a 5\% bounce rate (users interact with it) \\
  67\% of visits being were returning visitors \\
  284 overlays onto friends’ schedules (2 per user) \\
  \hline
\end{tabular}
\end{center}
\doublespacing

### 2016-04-13 design/usability.tex
Cite undergrads

Better CDCS provides two ways for users to export their schedule---as image or to Google calendar--except that the Google Calendar export feature is completely non-functional, telling users that ``{\tt This export tool will only work properly for the Spring of 2015}'' only \emph{after} they authorized the tool to access their Google account.

>>>>

Better CDCS provides two ways for users to export their schedule---as an image or to Google calendar---and the Google Calendar export feature is completely non-functional, telling users that ``{\tt This export tool will only work properly for the Spring of 2015}'' after the user authorizes the tool to access their Google account on a separate University page \cite{cdcs-google}.
